---
title: "Intro to Binomial"
author: "Nadia Aquil"
date: "5/2/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
library(ggplot2)
source("../R/functions.R")
```

# Binomial Package
The package "binomial" implements functions for calculating probabilities of a binomial random variable, as well as calculations for the probability distribution, expected value, variance, and other measures. 

## Calculating a probability
You can calculate the number of combinations in which k success can occur in n trials by using the function bin_choose()
```{r}
bin_choose(n = 5, k = 2)
```
You can calculate the probability of getting k success in n trials with a certain probability p of success by using bin_probability/
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = .5)
```

##Creating and plotting a binary distribution
You can use the function bin_distribution() to create a dataframe containing the values of the probability distribution for each possible number of successes. 
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)

#plot the distribution
plot(bin_distribution(trials = 5, prob = 0.5))
```

##Creating and plotting a cumulative binomial distribution
You can use the function bin_cumulative() to create a dataframe containing the values of the cumulative probability distribution for each possible number of
successes. 
```{r}
# binomial probability distribution
bin_cumulative(trials = 5, prob = 0.5)

#plot the distribution
plot(bin_cumulative(trials = 5, prob = 0.5))
```

