---
title: "Intro to Binomial"
author: "Nadia Aquil"
date: "5/2/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
library(ggplot2)
source("../R/functions.R")
```

# Binomial Package
The package "binomial" implements functions for calculating probabilities of a binomial random variable, as well as calculations for the probability distribution, expected value, variance, and other measures. 

## Calculating a probability
You can calculate the number of combinations in which k success can occur in n trials by using the function bin_choose()
```{r}
bin_choose(n = 5, k = 2)
```
You can calculate the probability of getting k success in n trials with a certain probability p of success by using bin_probability/
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = .5)
```

##Creating and plotting a binary distribution
You can use the function bin_distribution() to create a dataframe containing the values of the probability distribution for each possible number of successes. 
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)

#plot the distribution
plot(bin_distribution(trials = 5, prob = 0.5))
```

##Creating and plotting a cumulative binomial distribution
You can use the function bin_cumulative() to create a dataframe containing the values of the cumulative probability distribution for each possible number of
successes. 
```{r}
# binomial probability distribution
bin_cumulative(trials = 5, prob = 0.5)

#plot the distribution
plot(bin_cumulative(trials = 5, prob = 0.5))
```

##Creating a binomial random variable object
The function bin_variable() creates a binomial random variable object of class "binvar". It creates a object with a list of named elements of the variable object, such as number of trials, probability of success, and other summary statistics. By using the methods print, summary, or print.summary on this object, you can see the various statistics of the random variable object. 
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
bin_sum <- summary(bin1)
bin_sum
```

##Functions of measures
The binomial package also provides functions for each of the following measures: mean, variance, mode, skewness, and kurtosis. These functions are invoked as follows:

```{r}
#summary statistics binomial variable with 10 trials and .3 probability of success per trial
bin_mean(trials = 10, prob = .3)
bin_variance(trials = 10, prob = .3)
bin_mode(trials = 10, prob = .3)
bin_skewness(trials = 10, prob = .3)
bin_kurtosis(trials = 10, prob = .3)
```
